Appendix A: Feature comparison between `Distance` and other packages

### 2016-04-05 appendix-A.Rmd
revise markup and affiliation

---
author:
  - name: David L Miller
    affiliation: University of St Andrews
  - name: Eric Rexstad
    affiliation: University of St Andrews
  - name: Len Thomas
    affiliation: University of St Andrews
  - name: Laura Marshall
    affiliation: University of St Andrews
  - name: Jeffrey L Laake
    affiliation: Marine Mammal Laboratory
title: "Appendix A: Feature comparison between \\pkg{Distance} and other packages"
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: html_document
bibliography: jstatsoft.bib

>>>>

---
author:
  - name: David L Miller
    affiliation: Integrated Statistics and University of St Andrews
  - name: Eric Rexstad
    affiliation: University of St Andrews
  - name: Len Thomas
    affiliation: University of St Andrews
  - name: Laura Marshall
    affiliation: University of St Andrews
  - name: Jeffrey L Laake
    affiliation: Marine Mammal Laboratory
title: "Appendix A: Feature comparison between `Distance` and other packages"
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{booktabs}
output: html_document
bibliography: jstatsoft.bib
